%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Alexander} % Your first name
\familyname{Moore-Niemi} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Software Engineer}
\address{\#304, 804 Centre St}{Jamaica Plain MA 02130}
\mobile{(617) 833 7604}
\email{moore.niemi@gmail.com}
\extrainfo{http://mooreniemi.github.io/}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

\section{Objective}
\cvitem{}{Gain experience with large scale distributed systems.}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Keywords}

\cvitem{Fluent in}{Ruby}
\cvitem{Proficient in}{Java, Groovy, Javascript, Haskell}
\cvitem{Learning}{Go, C}
\cvitem{Frameworks}{Rails, Grails, Sinatra, Node.js, Ember}
\cvitem{Practices}{TDD, SOA, Pair programming, Functional programming, Kanban, Scrum, Agile}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Professional Experience}

\cventry{2016 -- }{Software Developer}{\textsc{Raizlabs}}{Boston}{}{Building web APIs from scratch to serve custom built mobile apps.}
\cvitem {2016}{Increased test coverage of Node.js web API for lifestyle app while implementing features such as comments. Comments implemented without using Sequelize's polymorphic relations.}{}
\cvitem {2016}{Increased performance while reducing LOC on key indexing actions in Ruby on Rails web API for healthcare app: from 800ms down to 250 ms. Check out \href{http://mooreniemi.github.io/2016/10/04/refactoring-away-from-statements-in-ruby.html}{my blog post "Refactoring away from statements in Ruby"} for a similar piece of refactoring that's open sourced.}{}

\cventry{2014 -- 2016}{Software Engineer}{\textsc{Zipcar}}{Boston}{}{Used Ruby and Java to build distributed systems with a REST architecture. On call and release engineer.}
\cvitem {2016}{"workerbee" project: A JRuby gem wrapping a Java microservices framework (using RabbitMQ as ESB). Included a cli tool that made it extremely easy for devs to create and deploy new services that ran in Java, with a Java framework, but were written from the dev's perspective entirely in Ruby..}{}
\cvitem {2016}{"Fleet API" project: An experimental API design exposing views rather than models. A surprising success that allowed both mobile and web frontends. I'm not convinced of it necessarily, but ask me about it--it's a unique case study.}{}
\cvitem {2016}{"New platform" project: SOA implementation of microservices on Java/Go PaaS via contributions to core inhouse framework and individual services. Authored a User service and an i18n service (based on gettext), both in Java.}{}
\cvitem {2015}{"Instant Drive" project: adding a new service and rebuilding parts of the core platform to support unlocking vehicles from our mobile phone app. Some work with Cassandra NoSQL, which taught me how not to use Cassandra.}{}
\cvitem {2015}{"Core API" project: transition away from shared models via gem to an ActiveResource-like pattern, loosening coupling to database. Preparatory work on monolithic architecture for decomposition into services. Our goal was to improve CI experience for devs, and we succeeded.}{}
\cvitem {2014}{"Pooling" project: extending "fleetsharing" with Avis cars while also improving vehicle availability. Required extensive redesign of original Zipcar data model, and was implemented as a Ruby on Rails API. A great example of tradeoffs in building a service instead of adding to a monolith.}{}


\cventry{2013 -- 2014}{Junior Software Engineer}{\textsc{PromoBoxx}}{Boston}{}{Development on front end and back end services in Ruby on Rails and Javascript integration.}

\cventry{2012 -- 2013}{Marketing Automation}{\textsc{WorldOne Interactive}}{Boston}{}{Scripting and data analysis for the marketing team.}
\cvitem {2012}{Used R for NLP to identify discussions in need of moderation. Patented use of NLP to identify physician discussions about pharmaceutical treatments.}{}

%----------------------------------------------------------------------------------------
%	OPEN SOURCE
%----------------------------------------------------------------------------------------

\section{Open Source}
\cvitem{\href{https://github.com/mooreniemi/graph\_function}{graph\_function}}{a Ruby gem to generate graphs of asymptotic performance}
\cvitem{\href{https://github.com/mooreniemi/array\_collapse}{array\_collapse}}{a Ruby C extension to add Array\#collapse, a method that allows blocks to be passed in to flatten}
\cvitem{\href{https://github.com/mooreniemi/proc\_compose}{proc\_compose}}{a Ruby C extension to add Proc\#compose (until it is added to Ruby core, which is on its way), a method for composing procs so that they can be passed in as a single block to any mapping operation}
\cvitem{\href{https://github.com/mooreniemi/figtree}{figtree}}{a Ruby gem for parsing ini\_files using parslet DSL}


%----------------------------------------------------------------------------------------
%	VOLUNTEER SECTION
%----------------------------------------------------------------------------------------

\section{Volunteering}

\cventry{2012 -- Now}{Transbucket.com}{Web Developer}{Migrated site from PHP to Ruby on Rails and implemented many new features. The premiere site for transgender surgery photos, with 90k users (~1k active uniques per month)}{}{}

%----------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%----------------------------------------------------------------------------------------

\section{Publications}

\cventry{2016}{Developer Testing: Building Quality into Software}{Addison-Wesley Signature Series}{}{A sidebar on how to think about types as a way of extending design by contract}{}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2012}{Certificate: Computation and Algorithms}{MIT}{Boston}{}{}
\cventry{2004--2009}{BFA Media Production}{Emerson College}{Boston}{Graduated with honors}{}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}